The Astropy Project:

### 2017-09-22 main.tex
Update on Overleaf.

\correspondingauthor{Astropy coordination committee}
\email{coordinators@astropy.org}

@@

\begin{itemize}
   \item The goal is to produce a brief and informative paper that covers major astropy principles not mentioned in the first paper, the core v2.0 package, and infrastructure in astropy project to support development in python.   
	\item We don't plan on including code in this paper, but if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository.
    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename} not ``Figure''
    \item If your subpackage was included in Paper I, then please just include a note on what the package does, a reference to paper I, and any new major updates to your package
    \item If your subpackage was not included, then please a further description of the sub-package on level with what was in the first paper, and highlight any major features in it.   Typically length should be equivalent to one column

@@

\subsection{Astropy development model, astropy ecosystem}
This subsection should include some basic statistics about the contributors, commits, line of code etc. up to the 2.0 release when we know it.

@@

\subsubsection{NDDdata}
% Matt C., Michael, or Steve C.
% Larry (nddata.utils)
NOTE (Larry), The package is nddata, which includes the NDData object.  Don't forget the nddata.utils functionality (e.g. Cutout2D, block\_reduce, etc.).

>>>>

\correspondingauthor{Astropy Coordination Committee}
\email{coordinators@astropy.org}

@@

\begin{itemize}
   \item The goal is to produce a brief and informative paper that covers major astropy principles not mentioned in the first paper, the core v2.0 package, and infrastructure in astropy project to support development in python.   
	\item We don't plan on including code in this paper, but if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository.
    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename} not ``Figure''
    \item If your subpackage was included in Paper I, then please just include a note on what the package does, a reference to paper I, and any new major updates to your package
    \item If your subpackage was not included, then please a further description of the sub-package on level with what was in the first paper, and highlight any major features in it.   Typically length should be equivalent to one column
    \item Please make sure you are logged into Overleaf or pushing a commit with your information to be able to track the contributors to the paper.

@@

\subsection{Coordination of Astropy}
% Kelle

\subsection{Astropy development model, astropy ecosystem}
% Erik 
This subsection should include some basic statistics about the contributors, commits, line of code etc. up to the 2.0 release when we know it.

@@

\subsubsection{NDDdata}
% Matt C., Michael, or Steve C.
% Larry (nddata.utils)
%NOTE (Larry), The package is nddata, which includes the NDData object.  %Don't forget the nddata.utils functionality (e.g. Cutout2D, block\_reduce, %etc.).
